---
output: 
  github_document
bibliography: [refs/forReadmeOnly.bib]
csl: refs/climaMod.csl
nocite: '@*'
---

```{r include=FALSE, eval = FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(),
  "rmarkdown", "bib2df", "shiny", "purrr", "yaml", "stringr"
), "refs/forReadmeOnly.bib")
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##>"
)
```

```{r, echo=F,  results="asis"}
img1_path <- "assets/logo.png"
if (file.exists(img1_path)) {
  cat(paste0("<img src=", img1_path, " align=\"right\" width=\"12%\">"))
}
```

# CV_yml <br></br>Rmarkdown for creating a CV <br></br><br></br><br></br>

The goal of CV_yml is to make an .html curriculum and .pdf using `yml` files.

To define languages and profiles, use the file `site/yml/shared_params.yml` (and `R/script_to_render_indiv_pdf.R`).

Use optionally the folder `site/figures` if you need any, and `.bib` files in the folder `site/bib`.

## folders: `data` and `config`

Fields in `site/yml/data` and `site/yml/config` yml files should match.
Use files in `site/yml/data` folder to add your information, and files in `site/yml/config` folder to configure how to show it.

## folder `dictionaries`

Chapters and field names for several languages are configured in folder `site/yml/dictionaries`

## `css` changes

After using custom classes  
modify files in folder `styles`  
and do:

```
library(sass)

sass(
  sass_file("site/styles/main.scss"),
  output = "site/css/style.css"
)
```
## Print CV to pdf file

```
# system terminal
# requires: node, npm
npm install puppeteer
```

```
# R
# Usage, function in R folder
# run in the root folder
source("R/render_single_Rmd.R")
render_single_Rmd("site/index.Rmd",
  location_site.yml = "site",
  output_dir = "simple_html_no_toc")

system(paste(
  "node js/print.js",
  file.path(getwd(), "simple_html_no_toc/index.html"),
  file.path(getwd(), "pdf/index_en_devel.pdf")
))
```

## Render site

* Use the code in `R/script_to_render_site.R`

## References

