---
output: 
  github_document
bibliography: [refs/forReadmeOnly.bib]
csl: refs/climaMod.csl
nocite: '@*'
---

```{r include=FALSE, eval = FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(),
  "rmarkdown", "bib2df", "shiny", "purrr", "yaml", "stringr"
), "refs/forReadmeOnly.bib")
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##>"
)
```

```{r, echo=F,  results="asis"}
img1_path <- "assets/logo.png"
if (file.exists(img1_path)) {
  cat(paste0("<img src=", img1_path, " align=\"right\" width=\"12%\">"))
}
```

# CV_yml <br></br>Rmarkdown for creating a CV <br></br><br></br><br></br>

The goal of CV_yml is to make an .html curriculum and .pdf using `yml` files.

## Example workflow

* Create two sibling folders, one of this repository and one with personal data.

``` bash
mkdir parent
cd parent
git clone https://github.com/fernandoroa/cv_yml
git clone https://gitlab.com/ferroao/curriculumpu
cd cv_yml
# open folder cv_yml in VSCode to run the scripts
code .

# Create _site (htmls)
# open and run R/script_to_render_site.R

# Create .pdf files
# open and run R/script_to_render_indiv_pdf.R
```

## folders: `data` and `config`

Fields in `curriculumpu/custom/yml/data` and `curriculumpu/custom/yml/config` yml files should match.
Use files in `curriculumpu/custom/yml/data` folder to add your information, and files in `curriculumpu/custom/yml/config` 
folder to configure how to show it.

## folder `dictionaries`

Chapters and field names for several languages are configured in folder `curriculumpu/custom/yml/dictionaries`

## `css` changes

After using custom classes in `.yml` files
modify files in folder `cv_yml/site/styles` or `curriculumpu/custom/styles`  

## Make .pdf documents

To define languages and profiles, use the file `curriculumpu/custom/yml/shared_params.yml` (and `cv_yml/R/script_to_render_indiv_pdf.R`).

Use optionally the folder `curriculumpu/custom/figures` if you need any, and `.bib` files in the folder `curriculumpu/custom/bib`.

* Use file `cv_yml/R/script_to_render_indiv_pdf`

## Render site

* Use the code in `cv_yml/R/script_to_render_site.R`

## Modify default Rmarkdown header

* Use `cv_yml/R/script_footer_generator`

## References

