---
output: 
  github_document
bibliography: [refs/forReadmeOnly.bib]
csl: refs/climaMod.csl
nocite: '@*'
---

```{r include=FALSE, eval = FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(),
  "rmarkdown", "bib2df", "shiny", "purrr", "yaml", "stringr"
), "refs/forReadmeOnly.bib")
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##>"
)
```

```{r, echo=F,  results="asis"}
img1_path <- "figures/logo.png"
if (file.exists(img1_path)) {
  cat(paste0("<img src=", img1_path, " align=\"right\" width=\"12%\">"))
}
```

# CV_yml <br></br>Rmarkdown for creating a CV <br></br><br></br><br></br>

To access this curriculum: https://ferroao.gitlab.io/curriculumpu

The goal of CV_yml is to make an .html curriculum using `yml` files and print it as .pdf files.

For several languages, use the file `_site.yml` (adding `index2.html`, etc. pages). 
Create `index*.Rmd`, to add language versions.

Use `config/...yml` to change display options.

Use optionally the folder `figures` if you need any, and `.bib` files in the folder `bib`.


## folders: `data` and `config`

fields in `data` and `config` yml files should match.
Use `data` to add your information, and config to configure how to show it.

## folder `names`

Chapters and field names for several languages are configured in folder `names`

## `css` changes

After using custom classes  
modify files in folder `styles`  
and do:

```
library(sass)

sass(
  sass_file("styles/main.scss"),
  output = "css/style.css"
)
```
## Print CV to pdf file

```
# system terminal
# requires: node, npm
npm install puppeteer
```

```
# R
# Usage, function in R folder
# run in the root folder
render_single_Rmd("index.Rmd", output_dir = "simple_html_no_toc")

system(paste(
  "node js/print.js",
  file.path(getwd(), "simple_html_no_toc/index.html"),
  file.path(getwd(), "pdf/index_en_devel.pdf")
))
```

## Summary

So all you have to do is:

* Clone this repository
* Use `_site.yml` and `index*.Rmd`to add languages.
* Modify `config` `.yml` files as desired
* If you want, also the `figures` folder and the `*.bib` files (folder `bib`)
* Having this types of files, press the "knit button" in Rstudio in `index.Rmd`, or use `rmarkdown::render_site()`
* For producing pdfs print with your internet browser

## References

